Learning and comparing functional connectomes across subjects

### 2013-01-01 paper.tex
Progress on conclusion

Horwitz \emph{el al.}\ \cite{horwitz1995} claimed almost 20 years ago
that ``the crucial concept needed for network analysis is covariance''.
In our eyes, this still holds today. Estimation of noiseless functional
connectomes relies largely on fitting covariance models.

>>>>

Horwitz \emph{el al.}\ \cite{horwitz1995} claimed almost 20 years ago
that ``the crucial concept needed for network analysis is covariance''.
In our eyes, this still holds today. Estimation functional connectomes
relies largely on fitting covariance models. Their comparison requires
understanding how these covariances vary and finding metrics to capture
this variability. Additionally, a secret ingredient to all statistical
steps is a good choice of confounds.

% XXX add here a bit more of connectome stuff. Be optimistic!
% Look to the future: note that estimation of connectomes with many nodes
% is more challenging than small connectomes, but that better apriori and
% better algorithms will push these limits further.

Reviewing methodological options to learn and compare connectomes
highlights that there is currently no unique solution, but a spectrum of
related methods and analysis strategies. More empirical results are
required to guide the choices, however this diversity is probably
unavoidable: a diffuse disease like schizophrenia will not lead to the
same connectome modifications as a focal lesion. In statistical learning,
``no free lunch'' theorems \cite{wolpert1996} tell us that no strategy
can perform uniformly better in all situations. In practice, the key to a
successful analysis is to understand well the assumptions and
interpretation of each option, in order to match the method to the
research question.
